\documentclass{beamer}

\usepackage{dirtytalk}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{color}
\definecolor{atomPurple}{RGB}{198,120,221}
\definecolor{atomRed}{RGB}{203,15,64}
\definecolor{atomGreen}{RGB}{0,128,0}
\definecolor{atomGreyLight}{RGB}{171,178,191}
\definecolor{atomGreyDark}{RGB}{92,99,112}
\definecolor{atomBlack}{RGB}{56,58,66}

\lstset{
language=C,
numbers=left,
showstringspaces=false,
tabsize=4,
columns=flexible,
keepspaces=true,
keywordstyle=\color{atomRed},
stringstyle=\color{atomGreen},
commentstyle=\color{atomGreyDark}
}

\title{Entity Linking for Fun and Profit}
\author{Vaughan Kitchen}
\date{May 29, 2019}

\begin{document}

\begin{frame}
\titlepage
\end{frame}

\begin{frame}{Structure}
	\begin{itemize}
		\item Background
		\item Techniques
		\item Maybe other stuff
		\item Maybe related Topics
	\end{itemize}
\end{frame}

\begin{frame}{Background}
	\begin{block}{Why}
		Bag of words models are only so good. Wouldn't it be nice if we could search semantically?
	\end{block}
	\begin{block}{What}
		User searches for ``michael motown first band"

		Entities ``Michael Jackson", ``Motown Records", ``The Jackson 5ive"
	\end{block}
	\begin{block}{How}
		\textit{entity-by-entity linking}, \textit{collective entity linking}, \textit{knowledge base}, \textit{graph theory}, \textit{neural networks}
	\end{block}
\end{frame}

\begin{frame}{Entity-by-Entity Linking}
	\begin{itemize}
		\item One word at a time
		\item Simple
		\item Fast
		\item Poor results
		\item Comes from DB theory
	\end{itemize}
\end{frame}

\begin{frame}{Collective Entity Linking}
	\begin{itemize}
		\item Uses context
		\item Link all words?
		\item How to detect entities?
		\item How to make fast?
		\item Neural network it?
	\end{itemize}
\end{frame}

\begin{frame}{How to Knowledge Base}
	\begin{itemize}
		\item Use Wikipedia
	\end{itemize}
\end{frame}

\begin{frame}{Queries and Documents}
	\begin{itemize}
		\item Queries don't use the same language as documents
		\item ``michael motown first band"
		\item Can they be linked the same way?
		\item Queries often short. Not enough context
		\item Results for partial disambiguation
		\item ``michael singer"
		\item ``George Michael", ``Michael Jackson", ``Michael Bublé", ``Michael Alan Singer (Author)"
		\item Best candidate?
		\item ``clinton falls asleep" $\rightarrow$ ``clinton falls $\vert$ asleep", ``clinton $\vert$ falls asleep"
	\end{itemize}
\end{frame}

\begin{frame}{Questions?}
\end{frame}

\end{document}
